Synthetic network and data generation using GeneNetWeaver(GNW)

### 2016-09-16 code/Rmd/synNetGen.Rmd
Minor modifications

knitr::opts_chunk$set(
  echo=FALSE,
  warning=FALSE,
  message=FALSE,
  error = FALSE,
  tidy = FALSE,
  cache = TRUE)
```

@@

# Create folder to store results
FOLD = Folder(name = 'Synthetic Networks', parentId = parentId)
FOLD = synStore(FOLD)
```
#### Extract network
```{r extractNet}
# Extract settings text file
con = file('../../../gnw//sandbox/settings.txt')
settings.txt = readLines(con)
close(con)

netSize = c(a = 1e1, b = 1e2, c = 1e3, d = 1e4)
for (net in names(netSize))){
  # Number of minimum regulators
  minReg = max(5, round(netSize[[net]]*0.5))

@@

  # Extract 10 subnetworks of size n from ecoli data
  system(paste('java','-jar','../../../gnw/gnw-3.1.2b.jar',
                 '--extract','-c',paste0(outputDir,'/settings.txt'), '--input-net',
                 '../../../gnw/sandbox/ecoli_transcriptional_network_regulonDB_6_7.tsv',
                 '--random-seed','--greedy-selection','--num-subnets=10',
                 paste0('--subnet-size=',netSize[[net]]),'--output-net-format=4',
                 paste0('--output-path=',outputDir),
                 paste0('--min-num-regulators=',minReg)))

@@

  # Change settings for simulations  
  tmp = settings.txt
  tmp[grep('outputDirectory = ', tmp)] = paste('outputDirectory =',outputDir)
  tmp[grep('ssDualKnockouts',tmp)] = "ssDualKnockouts = 0"
  tmp[grep('tsDREAM4TimeSeries',tmp)] = "tsDREAM4TimeSeries = 0"

  con = file(paste0(outputDir,'/settings.txt'))
  writeLines(tmp, con)
  close(con)

  # Simulate from extracted networks
  for (fnames in FNames){
    system(paste('java','-jar','../../../gnw/gnw-3.1.2b.jar',
                 '--simulate','-c',paste0(outputDir,'/settings.txt'), 
                 '--input-net', fnames, '--output-path',outputDir))

@@

    extractData <- function(pat,allfiles, file.name){
      read.table(allfiles[grep(paste0(file.name,pat),allfiles)], header=T, sep = '\t', quote='')
    }

@@

    # Set private acl to the gold standard file
    resAcc = ResourceAccess(principalId = 3319864, 
                            accessType = c('CREATE', 'READ', 'UPDATE', 'DELETE', 'CHANGE_PERMISSIONS', 'DOWNLOAD', 'UPLOAD', 'PARTICIPATE', 'SUBMIT', 'READ_PRIVATE_SUBMISSION', 'UPDATE_SUBMISSION', 'DELETE_SUBMISSION', 'TEAM_MEMBERSHIP_UPDATE', 'SEND_MESSAGE', 'CHANGE_SETTINGS'))
    acl = AccessControlList(id = OBJ$properties$id, resourceAccess = ResourceAccessList(resAcc))
    tmp = synCreateEntityACL(acl)

>>>>

knitr::opts_chunk$set(
  echo=FALSE,
  warning=FALSE,
  message=FALSE,
  error = FALSE,
  tidy = FALSE,
  cache = FALSE)
```

@@

# Create folder to store results
FOLD = Folder(name = 'Synthetic Networks', parentId = parentId)
FOLD = synStore(FOLD)
```
#### Extract network
```{r extractNet, cache=FALSE}
# Extract settings text file
con = file('../../../gnw//sandbox/settings.txt')
settings.txt = readLines(con)
close(con)

settings.txt[grep('ssDualKnockouts', settings.txt)] = "ssDualKnockouts = 0"
settings.txt[grep('ssMultifactorial', settings.txt)] = "ssMultifactorial = 0"
settings.txt[grep('tsDREAM4TimeSeries', settings.txt)] = "tsDREAM4TimeSeries = 0"
settings.txt[grep('simulateSDE', settings.txt)] = "simulateSDE = 1"

netSize = c(a = 1e2, b = 1500)
for (net in names(netSize)){
  # Number of minimum regulators
  minReg = max(5, round(netSize[[net]]*0.3))

@@

  # Extract 1 subnetworks of size n from ecoli data
  system(paste('java','-jar','../../../gnw/gnw-3.1.2b.jar',
                 '--extract','-c',paste0(outputDir,'/settings.txt'), '--input-net',
                 '../../../gnw/sandbox/ecoli_transcriptional_network_regulonDB_6_7.tsv',
                 '--random-seed','--greedy-selection','--num-subnets=1',
                 paste0('--subnet-size=',netSize[[net]]),'--output-net-format=4',
                 paste0('--output-path=',outputDir),
                 paste0('--min-num-regulators=',minReg)))

@@

  # # Change settings for simulations  
  # tmp = settings.txt
  # tmp[grep('outputDirectory = ', tmp)] = paste('outputDirectory =',outputDir)
  # tmp[grep('ssDualKnockouts',tmp)] = "ssDualKnockouts = 0"
  # tmp[grep('tsDREAM4TimeSeries',tmp)] = "tsDREAM4TimeSeries = 0"
  # 
  # con = file(paste0(outputDir,'/settings.txt'))
  # writeLines(tmp, con)
  # close(con)
  # 
  # Simulate from extracted networks
  for (fnames in FNames){
    system(paste('java','-jar','../../../gnw/gnw-3.1.2b.jar',
                 '--simulate','-c',paste0(outputDir,'/settings.txt'), 
                 '--input-net', fnames, '--output-path',outputDir))

@@

    extractData <- function(pat,allfiles, file.name){
      if (length(grep(paste0(file.name,pat),allfiles)) != 0)
        return(read.table(allfiles[grep(paste0(file.name,pat),allfiles)], header=T, sep = '\t', quote=''))
      else
        return(NULL)
    }

@@

    # # Set private acl to the gold standard file
    # resAcc = ResourceAccess(principalId = 3319864, 
    #                         accessType = c('CREATE', 'READ', 'UPDATE', 'DELETE', 'CHANGE_PERMISSIONS', 'DOWNLOAD', 'UPLOAD', 'PARTICIPATE', 'SUBMIT', 'READ_PRIVATE_SUBMISSION', 'UPDATE_SUBMISSION', 'DELETE_SUBMISSION', 'TEAM_MEMBERSHIP_UPDATE', 'SEND_MESSAGE', 'CHANGE_SETTINGS'))
    # acl = AccessControlList(id = OBJ$properties$id, resourceAccess = ResourceAccessList(resAcc))
    # tmp = synCreateEntityACL(acl)
